Trajectories

### 2021-09-20 Rmd/report.Rmd
fix fixed effets plots

## Vocabulary {.tabset .tab-pills}

### Vocabulary size {.tabset .tab-pills}

#### Comprehension

```{r vocabulary_comprehension, message=FALSE, warning=FALSE, paged.print=FALSE}

d <- vocabulary$wide %>% 
  filter(type=="Understands", modality != "Te")

ggplot(d, aes(age, prop, colour = lp, fill = lp)) +
  facet_wrap(~modality) +
  geom_point(size = 0.5, alpha = 0.21) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = FALSE) +
  labs(x = "Age (months)", y = "Vocabulary size (%)", colour = "LP", fill = "LP") +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +

  ggplot(d, aes(age, count, colour = lp, fill = lp)) +
  facet_wrap(~modality) +
  geom_point(size = 0.5, alpha = 0.21) +
  geom_smooth(method = "glm", method.args = list(family = "poisson"), se = FALSE) +
  labs(x = "Age (months)", y = "Vocabulary size (words)", colour = "LP", fill = "LP") +

  plot_layout(guides = "collect") &
  theme_github() +
  theme(
    legend.position = "top",
    legend.title = element_blank()
  )

#### Production

```{r vocabulary_production, message=FALSE, warning=FALSE, paged.print=FALSE}

vocabulary$wide %>% 
  filter(type=="Produces", modality != "Te") %>% 
  ggplot(aes(age, prop, colour = lp, fill = lp)) +
  facet_wrap(~modality) +
  geom_point(size = 0.5, alpha = 0.21) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = FALSE) +
  labs(x = "Age (months)", y = "Vocabulary size (%)", colour = "LP", fill = "LP") +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +

  vocabulary$wide %>% 
  filter(type=="Produces", modality != "Te") %>% 
  ggplot(aes(age, count, colour = lp, fill = lp)) +
  facet_wrap(~modality) +
  geom_point(size = 0.5, alpha = 0.21) +
  geom_smooth(method = "glm", method.args = list(family = "poisson"), se = FALSE) +
  labs(x = "Age (months)", y = "Vocabulary size (words)", colour = "LP", fill = "LP") +

  plot_layout(guides = "collect") &
  theme_github() +
  theme(
    legend.position = "top",
    legend.title = element_blank()
  )

#### {-}

#### {-}

@@

```{r loo_prod, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
loo_comp %>% 
  as_tibble() %>% 
  rownames_to_column("model") %>% 
  relocate(model, matches("elpd_loo"), matches("p_loo"), matches("looic"), matches("diff")) %>%
  mutate_all(as.numeric) %>% 
  gt() %>% 
  tab_spanner(md("**LOO<sub>ELPD</sub>**"), matches("elpd_loo")) %>% 
  tab_spanner(md("**LOO<sub>p</sub>**"), matches("p_loo")) %>% 
  tab_spanner(md("**LOO<sub>IC</sub>**"), matches("looic")) %>% 
  tab_spanner(md("**LOO<sub>diff</sub>**"), matches("diff")) %>% 
  fmt_number(3:13) %>% 
  cols_label(
    model = "Model",
    # elpd
    elpd_loo = md("*ELPD*"),
    se_elpd_loo = md("*SE*"),
    subsampling_se_elpd_loo = md("*SE<sub>sub</sub>*"),
    # p
    p_loo = md("*p*"),
    se_p_loo = md("SE"),
    subsampling_se_p_loo = md("SE<sub>sub</sub>"),
    # looic
    looic = md("*LOO-IC*"),
    se_looic = md("*SE*"),
    subsampling_se_looic = md("SE<sub>sub</sub>"),
    # diff
    elpd_diff = md("*diff*"),
    se_diff = md("*SE*"),
    subsampling_se_diff = md("*SE<sub>sub</sub>*"),
  ) %>% 
  as_raw_html()
```

@@

post <- gather_draws(fits_comp$fit_2, `b_.*`, regex = TRUE) %>% 
  mutate(.value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4))

ggplot(post, aes(.value)) +
  facet_wrap(~.variable, scales = "free_x") +
  geom_vline(xintercept = 0, size = 1, colour = "grey") +
  stat_histinterval(fill = "white") +
  labs(x = "Value", y = "Posterior probability density", fill = "Variable") +
  theme_github() +
  theme(
    legend.position = "none",
    plot.caption.position = "plot",
    plot.caption = element_text(hjust = 0),
    # axis.text = element_text(size = 7),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  )
```

@@

post <- gather_draws(fits_prod$fit_2, `b_.*`, regex = TRUE) %>% 
  mutate(.value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4))

ggplot(post, aes(.value)) +
  facet_wrap(~.variable, scales = "free_x") +
  geom_vline(xintercept = 0, size = 1, colour = "grey") +
  stat_histinterval(fill = "white") +
  labs(x = "Value", y = "Posterior probability density", fill = "Variable") +
  theme_github() +
  theme(
    legend.position = "none",
    plot.caption.position = "plot",
    plot.caption = element_text(hjust = 0),
    # axis.text = element_text(size = 7),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  )
```

>>>>

@@

```{r loo_prod, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
loo_prod %>% 
  as_tibble() %>% 
  rownames_to_column("model") %>% 
  relocate(model, matches("elpd_loo"), matches("p_loo"), matches("looic"), matches("diff")) %>%
  mutate_all(as.numeric) %>% 
  gt() %>% 
  tab_spanner(md("**LOO<sub>ELPD</sub>**"), matches("elpd_loo")) %>% 
  tab_spanner(md("**LOO<sub>p</sub>**"), matches("p_loo")) %>% 
  tab_spanner(md("**LOO<sub>IC</sub>**"), matches("looic")) %>% 
  tab_spanner(md("**LOO<sub>diff</sub>**"), matches("diff")) %>% 
  fmt_number(3:13) %>% 
  cols_label(
    model = "Model",
    # elpd
    elpd_loo = md("*ELPD*"),
    se_elpd_loo = md("*SE*"),
    subsampling_se_elpd_loo = md("*SE<sub>sub</sub>*"),
    # p
    p_loo = md("*p*"),
    se_p_loo = md("SE"),
    subsampling_se_p_loo = md("SE<sub>sub</sub>"),
    # looic
    looic = md("*LOO-IC*"),
    se_looic = md("*SE*"),
    subsampling_se_looic = md("SE<sub>sub</sub>"),
    # diff
    elpd_diff = md("*diff*"),
    se_diff = md("*SE*"),
    subsampling_se_diff = md("*SE<sub>sub</sub>*"),
  ) %>% 
  as_raw_html()
```

@@

var_levels <- c("b_Intercept", "b_age", "b_frequency_center", "b_lp1", "b_cognate1", "b_cognate2", "b_lp1:cognate1", "b_lp1:cognate2")
var_labels <- c("Intercept", "Age (+1 month)", "Frequency (+1 SD)", "Lang. Profile (Bil. - Mon.)", "Cognateness 1 (IDC+NIC - NC)", "Cognateness 2 (IDC -NIC)", "Lang. Profile \u00d7 Cognateness 1", "Lang. Profile \u00d7 Cognateness 2")
post <- gather_draws(fits_comp$fit_2, `b_.*`, regex = TRUE) %>% 
  mutate(
    .value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4),
    .variable = factor(.variable, levels = var_levels, labels = var_labels, ordered = TRUE)
  )

ggplot(post, aes(.value, fct_rev(.variable))) +
  geom_vline(xintercept = 0, size = 0.75, colour = "grey") +
  stat_pointinterval(colour = "white") +
  labs(x = "Comprehension posterior probability", y = "Variable", fill = "Variable") +
  scale_x_continuous(labels = percent) +
  theme_github() +
  theme(
    legend.position = "none",
    plot.caption.position = "plot",
    plot.caption = element_text(hjust = 0),
    axis.title.y = element_blank(),
    # axis.text = element_text(size = 7),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.major.y = element_blank()
  )
```

@@

var_levels <- c("b_Intercept", "b_age", "b_frequency_center", "b_lp1", "b_cognate1", "b_cognate2", "b_lp1:cognate1", "b_lp1:cognate2")
var_labels <- c("Intercept", "Age (+1 month)", "Frequency (+1 SD)", "Lang. Profile (Bil. - Mon.)", "Cognateness 1 (IDC+NIC - NC)", "Cognateness 2 (IDC -NIC)", "Lang. Profile \u00d7 Cognateness 1", "Lang. Profile \u00d7 Cognateness 2")
post <- gather_draws(fits_prod$fit_2, `b_.*`, regex = TRUE) %>% 
  mutate(
    .value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4),
    .variable = factor(.variable, levels = var_levels, labels = var_labels, ordered = TRUE)
  )

ggplot(post, aes(.value, fct_rev(.variable))) +
  geom_vline(xintercept = 0, size = 0.75, colour = "grey") +
  stat_pointinterval(colour = "white") +
  labs(x = "Production posterior probability", y = "Variable", fill = "Variable") +
  scale_x_continuous(labels = percent) +
  theme_github() +
  theme(
    legend.position = "none",
    plot.caption.position = "plot",
    plot.caption = element_text(hjust = 0),
    axis.title.y = element_blank(),
    # axis.text = element_text(size = 7),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.major.y = element_blank()
  )
```
